\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-20 doc/sw-system.tex
Section 6 comments including substantive sentence

In some cases the rejection of the false negatives is understandable: the
lensed features are faint, or in some cases, somewhat unrealistic as lenses.
However, in other cases a reasonably obvious lens was passed over.  This
mainly seems to be due to noise in the system: when only low-skill classifiers
view a subject, all the updates to its posterior probability are small, and if
none are very confident about the presence of lensing, the subject follows a
random walk down its trajectory plot. This can be seen in the top left panel
of the figure.

@@

Some of  the mistakes made by reasonably high skill
classifiers working at high speed
could have perhaps been corrected by those classifiers themselves, had
they had access to a ``go back'' option. While clearly enabling error
reduction, we might worry about such a mechanism enabling classifiers to have
a guess, then go and read the Talk discussion, and then return to the
classification interface to change their mind to agree with the forum. In
fact, this is already possible on the current interface -- and indeed, it is
not obvious that such correlations would necessarily lead to poorer system
performance. This could be tested by presenting a fraction of the volunteers
with a version of the site that actively suggested that they take this
approach, and then tracking the relative performance of ``collaborative''
classifications compared with independent ones. We leave the exploration of
this to further
work.

>>>>

In some cases the rejection of the false negatives is understandable: the
lensed features are faint, or in some cases, appear somewhat unrealistic compared to real lenses.
However, in other cases a reasonably obvious lens was passed over.  This
mainly seems to be due to noise in the system: when only low-skill classifiers
view a subject, all the updates to its posterior probability are small, and if
none are very confident about the presence of lensing, the subject follows a
random walk down its trajectory plot. This can be seen in the top left panel
of Figure \Fref{fig:discuss:performance:trajectories}.

@@

Some of  the mistakes made by reasonably high skill
classifiers working at high speed
could have perhaps been corrected by those classifiers themselves, had
they had access to a ``go back'' option. While clearly enabling error
reduction, we might worry about such a mechanism enabling classifiers to have
a guess, then go and read the Talk discussion, and then return to the
classification interface to change their mind to agree with the forum. In
fact, this is already possible on the current interface -- and indeed, it is
not obvious that such correlations would necessarily lead to poorer system
performance. There may well also be effects on user confidence; it may be that encouraging this sort of checking would result in increased and not necessarily productive caution. This could be tested by presenting a fraction of the volunteers
with a version of the site that actively suggested that they take this
approach, and then tracking the relative performance of ``collaborative''
classifications compared with independent ones. We leave the exploration of
this to further
work.
